Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-01 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
little changes

In Figures &nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

@@

Additionally, assuming a \SI{5}{\percent} threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests. This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and &nbsp;\ref{fig:lake_0.05}(a).

>>>>

In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Values below  $0.05$  are represented by dark areas, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.
```{r real_images_test_Mexico, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Coast of Jalisco: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

@@

Additionally, assuming a \SI{5}{\percent} threshold for $p$-values, in most cases, the heterogeneous regions detected by the $S_{\widetilde{H}{\text{AO}}}(\bm{Z}; L)$ test were more extensive than those detected by the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ tests. This was mainly observable in Figures&nbsp;\ref{fig:sim_SAR_Images_p05}(a), &nbsp;\ref{fig:Mexico_crops_0.05}(a), and&nbsp;\ref{fig:lake_0.05}(a).
